%-------------------------
% Resume in Latex
% Author : Franco Serio
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/tanoargie}{\Large Franco Serio}} & Email : \nolinkurl{francoagustinserio@gmail.com}\\
  \nolinkurl{https://github.com/tanoargie}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {School of Exact and Natural Sciences - UBA}{}
      {Master of Science in Computer Science}{2014 -- abandoned}
    \resumeSubheading
      {Highest College - Hull Cordell}{}
      {High School}{2013}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Thirdlove}{}
      {Software Engineer}{Jun 2022 - July 2023}
      \break
      {Shopify-based e-commerce. Worked both in the theme, using vanilla Javascript and React, and also on configuring the serverless backend using multiple AWS services. Used Python (for data) and NodeJS (for web) Lambda functions and set up CloudWatch logs. Integration with several event-based providers like Sailthru (for email) or Attentive (for SMS) and AWS SNS service. Migrated some services to use CloudFormation in order to streamline deployment. Also migrated some sites in EC2 to use Shopify pages.}

    \resumeSubheading
      {Rocket Insights}{}
      {Software Engineer}{Jun 2021 - Jun 2022}
      \resumeItemListStart
        \resumeItem{Moody's}
          {Working in the moody's lending Angular/.NET web-app project.}
        \resumeItem{Simplisafe}
          {Working in the company's Gatsby based e-commerce site mainly. Used Contentful CMS as a database.}
      \resumeItemListEnd

    \resumeSubheading
      {Amalgama}{}
      {Software Engineer}{Dec 2018 - Jun 2021}
      \resumeItemListStart
        \resumeItem{BigFive}
          {Worked in front-end features both in the web-app dashboard made in ReactJS and the mobile application made in React-Native.}
        \resumeItem{Honeycomb}
          {I was the backend developer of this web application made entirely in NodeJS with HapiJS framework and a MongoDB database in Atlas. Backend deployed using AWS Beanstalk. Also installed configured Jenkins server for CI/CD right from the start. Frontend in ReactJS with Redux and deployed in AWS with S3.}
	      \resumeItem{Quadminds}
          {As a Wordpress developer I added some features to the site.}
	      \resumeItem{Repasar}
          {Web based application for online tutoring made in ReactJS with SSR. Also configured Gitlab CI/CD with Slack and AWS EC2 integration.}
	      \resumeItem{VeryBusy}
          {Rails developer for a web-based collaboration tool for retouchers and photographers. Others technologies used include PostgresQL.}
	      \resumeItem{MiBA}
          {Django backend-developer in a mobile application aimed at helping the citizens of the City of Buenos Aires. Backed with a MySQL database.}
      \resumeItemListEnd

  \resumeSubheading
      {Botmaker}{}
      {Software Engineer}{Jan 2018 - Dec 2018}
      \resumeItemListStart
        \resumeItem{Botmaker.com}
          {Botmaker is a SaaS chatbot platform. Here I worked as a ReactJS developer expanding the site with new features for our clients. Frontend deployed in Cloud Storage in GCP.}
        \resumeItem{Botmaker Engine}
          {Worked in the engine as a Java and NodeJS backend developer with Postgres database and Google BigQuery for big data. First introduction to GCP ecosystem using Cloud Functions.}
      \resumeItemListEnd

  \resumeSubheading
      {Sarsy}{}
      {Jr. Software Developer}{Jun 2016 - Jun 2017}
      \resumeItemListStart
        \resumeItem{Gedeco}
          {Web application to help inspectors to ensure buildings don\/'t have irregularities. This was made in the .Net framework with VB and SQL Server.}
        \resumeItem{Vicente L\'opez Hospital}
          {Windows desktop application developed in C\# for the administration of the Bernardo Houssay hospital.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Some Personal Projects}
 \resumeSubHeadingListStart
   \resumeSubItem{La Botonera Argenta}
     {NextJS web-app displaying sounds from famous argentinians. Backed with NestJS. Deployed in GCP, first using Cloud Run and Cloud SQL (PostgresQL) but then migrated to a dockerized app inside a Compute Engine's VM. Cloud Storage is used for saving user's audios and Google DNS for mapping domains. It's online at \nolinkurl{https://botonera-argenta.com.ar}}
   % \resumeSubItem{Samser}
   %   {Rails web-app with a front-end in VueJS aimed at pet owners and vets. Using Google's Compute Engine for deployment and Google DNS. Also online at \nolinkurl{https://samser.co}}
   \resumeSubItem{Tipeo Nada}
     {SDL2 game to practice typewriting. Compiled for web with Emscripten. You can check it at \nolinkurl{https://storage.googleapis.com/tipeo-nada-web/TipeoNadaWeb.html}.}
   \resumeSubItem{Argentina Movie Theatres}
     {An API Endpoint in NestJS to get the movie schedules of the 3 main cinema chains in Argentina. Deployed in RapidAPI with a free tier. Can check it at \nolinkurl{https://rapidapi.com/franco-73xZwCbjr/api/argentina-movie-theatres}.}
   \resumeSubItem{Youtrmr}
     {Rust CLI application to trim a youtube video and download it. You can find it at \nolinkurl{https://github.com/tanoargie/youtube-trimmer/}.}
   \resumeSubItem{Youtrmr-Web}
     {Wanted to try out Nuxt framework, so I created a web-based application to apply Youtrmr and deployed it in GCP. Called it \nolinkurl{https://youtrmr.samser.co}.}
   \resumeSubItem{El Rincón del Tano}
     {Personal Blog made in Gatsby. Called it \nolinkurl{https://elrincondeltano.com}.}
   \resumeSubItem{Samext}
     {Chrome extension. Can check it out at \nolinkurl{https://chromewebstore.google.com/detail/samext/folkogmaemenfaebhgdnpkminckfppdd?hl=es} and code open-sourced at \nolinkurl{https://github.com/tanoargie/samext}.}
   \resumeSubItem{Samratings}
     {Small prototype to test ActionCable in Ruby on Rails. It displays the current viewership from Twitch and Youtube from 7 popular channels. Deployed to test it at https://samratings.samser.co/.}
 \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, Javascript, C++, SQL, Latex, Ruby, HTML, CSS}
    }
    \item{
      \textbf{Technologies}{: AWS, GCP, NodeJS, ReactJS, Django, Rails, Docker, Nginx, Vim, Unix, Gitlab CI/CD, React Native, Postgres, MySQL, Linux}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------

%--------Languages------------
\section{Languages}
  {Spanish (Native), English (Full Professional), Italian (Basic)}

%-------------------------------------------
\end{document}
